---
title: "Animal Care & Control Data Analysis: South Bend"
output: html_document
---
#Introduction
This is the first in a series of reports, attempting to show which datasets are publicly available in my hometown of South Bend, Indiana.
My motivation for this project is twofold: the first objective is to stress the importance of robust open data and the second is to highlight the improvements that are necessary for South Bend's Open Data Portal.

With that out of the way, this first report will cover the "Animal Care and Control Monthly Statistics" dataset, located [here](http://data-southbend.opendata.arcgis.com/datasets/7176100434074f48adf40747b6bc1e70_0). 

```{r Initial-Analysis, echo=FALSE}
setwd("~/ODV/AnimalControl-SB")
dat = read.csv("Animal_Care_and_Control_Monthly_Statistics.csv")
dat = na.omit(dat) #removing NA's 
dat.final = dat[,c(-2,-7)] # removed year column which contained only 2014 and FID column which is identical to month column

```

After loading the data with some slight manipulations, it will be helpful for us to see the summary statistics of the columns.

```{r}
summary(dat.final)
```

The first column simply contains the months of one year, but the summaries for the other columns tell us that in 2014 there was an average 
of 25 adoptions, about 30 pets returned home, and about 17 bite cases serviced per month. The rescue/rehab transfer out column seems to be tail heavy with
#Plots 

```{r Plots, echo=FALSE}
plot(dat.final$Adoptions~dat.final$Month, xlab= "Month", ylab="# of Adoptions", main="Monthly Adoptions")
plot(dat.final$Bite_Cases_Serviced_by_SBACC~dat.final$Month, xlab= "Month", ylab="# of Bite Cases", main="Monthly Bite Cases")
plot(dat.final$Pets_Returned_Home~dat.final$Month, xlab= "Month", ylab="# of Pets Returned Home", main="Monthly Pets Returned Home")
```

#Analysis 

```{r Analysis, echo=FALSE}

```

